A Reduced Order Model for Porous Media Flows: Coupling Linear Regression with Principal Component Analysis (PCA) using High-Order Singular Value Decomposition (HOSVD) in Upscaling Calculations for Permeability in Reservoir Simulations

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

As already mentioned, four upscaled permeability field models were obtained from the high-resolution (\ie the BaseCase) permeability field. When compared to the BaseCase model, all the upscaled models were upgridded to reduce the resolution of the permeability field (Fig.~\ref{fig:HiRes_LowRes_Mesh}). The first two upscaled models are arithmetic and harmonic averaging methods  (referred to as ArithMean and HarmMean, respectively).

In both sets of test-cases, averages are calculated for each block using the $1600$ data points from the blocks of the BaseCase to obtain a permeability value for each block in the upscaled models. This effectively homogenizes the permeability field in each block. The upscaled permeability field for the third and fourth cases are referred to as PDFCase and PCA-LinReg Case, respectively. And, as can be deduced from the names, these cases are based on probability density function (PDF) and SVD, respectively. The description for these permeability field models are presented in Sections~\ref{subsubsection:pdfcase_preprocess_algorithm} and ~\ref{subsubsection:svdcase_preprocess_algorithm} respectively. It is appropriate to note that although these models (PDFCase and PCA-LinReg Case) are upscaled, they retain heterogeneity within the blocks.

>>>>

As previously mentioned, four upscaled techniques applied to permeability dataset were obtained from the high-resolution (\ie the BaseCase) configuration. Prior to upscaling, mesh resolution of the BaseCase configuration was coarsened, Fig.~\ref{fig:HiRes_LowRes_Mesh}, in which the number of triangular elements was reduced from 4112 to 728. Arithmetic (ArithMean) and harmonic (HarmMean) averaging methods were initially applied to the BaseCase configuration. In both sets of test-cases, averages are calculated for each block using the $1600$ data points from the blocks of the BaseCase to obtain permeability values for each block in the upscaled models. This effectively homogenized the permeability dataset in each block. Permeability dataset was also upscaled using probability density function (PDFCase) and SVD (PCA-LinReg Case). Description of these models are introduced in Sections~\ref{subsubsection:pdfcase_preprocess_algorithm}-\ref{subsubsection:svdcase_preprocess_algorithm}. Different from ArithMean and HarmMeanand, PDFCase and PCA-LinReg Case are able to retain heterogeneity within each block.
